Exploration

### 2018-03-14 exploration.Rmd
added function for summarizing IPM simulations

#---- Realization: use estimated slopes to generate simulated data
S.i <- vector("list", n_sim)
for(s in 1:n_sim) {
  S.i[[s]] <- simulate_data(n.cell, tmax, n0, z.rng, U.f$lo, U.f$hi, 
                     p.ipm, X, n_z, sdd.pr, U.f$sdd.j, verbose=T)
  cat("||-- Finished simulation", s, "\n||--\n")
}
S.sum <- list(B=map(S.i, ~.$B),
              nSd=map(S.i, ~.$nSd),
              D=map(S.i, ~.$D),
              p_est=map(S.i, ~.$p_est.i),
              N_sim=map(S.i, ~.$N_sim),
              N_tot=map(S.i, ~map_dbl(.$d, 
                                    ~sum(!is.na(.$sizeNext[.$yr==tmax])))),
              N_surv=map(S.i, ~map_dbl(.$d, 
                                    ~sum(.$surv[.$yr==tmax], na.rm=T))),
              N_rcr=map(S.i, ~map_dbl(.$d, 
                                    ~sum(is.na(.$size[.$yr==tmax]))))) %>% 
  map(simplify2array)
rm(S.i)

S.f <- list(B.mn=apply(S.sum$B, c(1,2), mean), 
            B.sd=apply(S.sum$B, c(1,2), sd), 
            nSd.mn=apply(S.sum$nSd, c(1,2), mean), 
            nSd.sd=apply(S.sum$nSd, c(1,2), sd), 
            D.mn=apply(S.sum$D, c(1,2), mean), 
            D.sd=apply(S.sum$D, c(1,2), sd), 
            p_est.mn=apply(S.sum$p_est, c(1,2), mean), 
            p_est.sd=apply(S.sum$p_est, c(1,2), sd), 
            N_sim.mn=apply(S.sum$N_sim, c(1,2), mean), 
            N_sim.sd=apply(S.sum$N_sim, c(1,2), sd),
            N_tot.mn=apply(S.sum$N_tot, 1, mean),
            N_tot.sd=apply(S.sum$N_tot, 1, sd),
            N_surv.mn=apply(S.sum$N_surv, 1, mean),
            N_surv.sd=apply(S.sum$N_surv, 1, mean),
            N_rcr.mn=apply(S.sum$N_rcr, 1, mean),
            N_rcr.sd=apply(S.sum$N_rcr, 1, mean))

>>>>

#---- Realization: use estimated slopes to generate simulated data
S.i <- vector("list", n_sim)
for(s in 1:n_sim) {
  S.i[[s]] <- simulate_data(n.cell, tmax, n0, z.rng, U.f$lo, U.f$hi, 
                     p.ipm, X, n_z, sdd.pr, U.f$sdd.j, verbose=T)
  cat("||-- Finished simulation", s, "\n||--\n")
}
S.f <- summarize_IPM_simulations(S.i)
